---
title: "Untitled"
output: html_document
---
# PURPOSE 
The only purpose of this script is to find a bunch of indicators that I can use in a purrr worked example.

# METHODOLOGY
- get the list of indicators by area type
- get the list of unique indicators
- join them
- filter to find those indicators which area available for Ward, LTLA, UTLA, and Region
- eyeball the result to select some indicators to play with


```{r}
library(fingertipsR)
library(dplyr)
library(purrr)
```


# One time script to identify suitable indicators to work with
```{r}
inds_by_area <- indicator_areatypes()
area_types <- area_types()
unique_inds <- indicators_unique()

ind_and_area_data <- inds_by_area %>%
  left_join(area_types) %>%
  left_join(unique_inds) %>%
  select(IndicatorID,
         IndicatorName,
         AreaTypeID,
         AreaTypeName,
  ) %>%
  distinct() 

# find indicators which are available for Ward, LTLA, UTLA, and Region
inds_all_area_types <- ind_and_area_data %>%
  filter(IndicatorID %in% subset(ind_and_area_data,AreaTypeName == "Ward",IndicatorID)$IndicatorID
         & IndicatorID %in% subset(ind_and_area_data,AreaTypeName == "Upper tier local authorities (post 4/21)",IndicatorID)$IndicatorID
         & IndicatorID %in% subset(ind_and_area_data,AreaTypeName == "Lower tier local authorities (post 4/21)",IndicatorID)$IndicatorID
         & IndicatorID %in% subset(ind_and_area_data,AreaTypeName == "Government Office Region",IndicatorID)$IndicatorID
  )
```


## Selection
The following indicators are available for Ward, LTLA, UTLA, and Region, and give us something interesting to work with

IID     | Indicator
--------|------------------------------------------------------------------------------------
93106   | Reception: Prevalence of overweight (including obesity), 3-years data combined
93108   | Year 6: Prevalence of overweight (including obesity), 3-years data combined
93553   | Deprivation score (IMD 2019)

