---
title: "Purrr example using NCMP data"
author: "MP"
date: "19/11/2021"
output: html_document
---

```{r}
library(fingertipsR)
library(dplyr)
library(purrr)
```


## Selection
The following indicators are available for Ward, LTLA, UTLA, and Region, and give us something interesting wo work with

IID     | Indicator
--------|------------------------------------------------------------------------------------
93106   | Reception: Prevalence of overweight (including obesity), 3-years data combined
93108   | Year 6: Prevalence of overweight (including obesity), 3-years data combined
93553   | Deprivation score (IMD 2019)


AreaTypeID      | AreaType
----------------|-----------
6               | GOR
8               | Ward
401             | LTLA
402             | UTLA


## Define constants
```{r}
# Define the indicator ID's that we care about
iwca <- c(93106, 93108, 93553)

# Define the area type ID's that we care about
atwca <- c(6,8,401,402)
```

## Create the argument tibble for purrr::map2_dfr
purrr::map2_dfr takes two arguments, in this example IndicatorID and AreaTypeID. We need to supply a table with every combination of those two arguments that we want to be iterated over.
```{r}
# Create a list with the indicators and area types (required to create the cross arg's, which is required for map2)
argList <- list(IndicatorID = iwca, AreaTypeID = atwca)

# Create a cross argument tibble, listing every possible combination of the two variables, (which is required for map2)
crossArg <- cross_df(argList)
```

## Create function
The purrr::map2_dfr function wants to be supplied with two arguments, in the correct order.
For the sake of simplicity, we'll create a simplified version of the fingertips_data function, stating that we'll pass in area type ID as the 1st argument, and indicatorID as the 2nd

```{r}
fn_ftd <- function(aty, iid){
  fingertips_data(AreaTypeID = aty, IndicatorID =iid,)
}
```


# READ
```{r}
myData <- map2_dfr(crossArg$AreaTypeID, crossArg$IndicatorID, fn_ftd)

ft_data <- myData %>% 
  select(IndicatorID, 
         IndicatorName,
         ParentCode,
         ParentName,
         AreaType, 
         AreaCode, 
         AreaName, 
         Timeperiod, 
         Value, 
         TimeperiodSortable) %>% 
  distinct()
```
